On mapping errors and seeding heuristics for DNA alignment

### 2019-04-16 MEM.tex
Updated affiliations and acknowledgements according to instructions.

\author[1,2]{Guillaume J. Filion}
\author[1,2]{Ruggero Cortini}
\author[1,2]{Eduard Zorita}
\affil[1]{Genome Architecture, Gene Regulation, Stem Cells and Cancer
Programme, Center for Genomic Regulation (CRG), The Barcelona Institute of
Science and Technology, Dr. Aiguader 88, Barcelona 08003, Spain.}
\affil[2]{University Pompeu Fabra, Doctor Aiguader, 08003 Barcelona,
Spain.}

@@

We acknowledge the financial support of the Spanish Ministry of Economy and
Competitiveness (‘Centro de Excelencia Severo Ochoa 2013-2017’, Plan Nacional
BFU2012-37168), of the CERCA Programme~/~Generalitat de Catalunya, and of the
European Research Council (Synergy Grant 609989). R.~C.~ was supported by the
People Programme (Marie Curie Actions) of the European Union's Seventh Framework
Programme (FP7/2007-2013) under REA grant agreement 608959.

>>>>

\author[1,2]{Guillaume J. Filion}
\author[1]{Ruggero Cortini}
\author[1]{Eduard Zorita}
\affil[1]{Center for Genomic Regulation (CRG), The Barcelona Institute of
Science and Technology, Dr. Aiguader 88, Barcelona 08003, Spain.}
\affil[2]{University Pompeu Fabra (UPF), Barcelona, Spain.}

@@

We acknowledge the financial support of the Spanish Ministry of Economy,
Industry and Competitiveness (`Centro de Excelencia Severo Ochoa
2013-2017', Plan Nacional BFU2012-37168), of the CERCA
Programme~/~Generalitat de Catalunya, and of the European Research Council
(Synergy Grant 609989). R.~C. was supported by the People Programme
(Marie Curie Actions) of the European Union's Seventh Framework Programme
(FP7/2007-2013) under REA grant agreement 608959. We also acknowledge
support of the Spanish Ministry of Economy and Competitiveness (MEIC) to
the EMBL partnership.
